Ancestry linkage in hybrid zones

### 2016-02-06 drafts/hybrid_zone.tex
added Figure1

%As an approximation, we consider a cline of narrow width (look up cline width for underdominance, Barton/May?), such that the frequency of migrant alleles is exponential and negligible at distance away from the center of the hybrid zone. This means that recombination events that occur away from the center of the zone do not result in a change in $a$.

>>>>

\begin{figure}
\includegraphics{figs/BM_schematic}
\caption{A cartoon representation of the model. The black line represents the path, backwards in time, of a selected site that is sampled in the present day ($\tau=0$). The center of the hybrid zone is defined at geographic position $x=0$, such that ancestry A is less fit at $x>0$ and ancestry B is less fit when $x<0$. In this figure, the sampled allele under selection is of ancestry B, and as a result migrates rapidly back to $x>0$ from a position $x<0$. Red dots represent recombination events along the entire haplotype, and here lineages that recombine off the same initial haplotype as the selected allele are represented by colored lines. Here, the initial haplotype is only broken up into 3 chunks over 100 generations. Recombination events can cause these chunks to change linkage to the allele at the selected locus (e.g. a chunk that was initially linked to a selected allele of ancestry A can become linked to a selected allele of ancestry B). Here, yellow lineages are linked to an allele of ancestry A at the selected locus, and blue lineages are linked to an allele of ancestry B. The ancestry of the blue and yellow lineages are determined by their position at $\tau=100$. Here the left-most yellow lineage is of ancestry A and the blue lineage is of ancestry B.  }\label{Fig:schematic}
\end{figure}
%As an approximation, we consider a cline of narrow width (look up cline width for underdominance, Barton/May?), such that the frequency of migrant alleles is exponential and negligible at distance away from the center of the hybrid zone. This means that recombination events that occur away from the center of the zone do not result in a change in $a$.
